The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2024-01-17 MS_ToSubmit/RevisedVersion.Rmd
Add Freeman 1978

Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
Considering the relationship between this property and TL in the food web of the MPA N-BB, it is worth to highlight that species with the highest closeness values are low-TL consumers (TL = 2 - 3): species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda. Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], and the warming trend reported for the surface and subsurface waters in the Southwest Atlantic Ocean [@Franco2020a; @Galvan2022a], should be of concern since it might reach many other species in the food web.
Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010]. We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense. Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides* (juveniles), the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem. All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].

>>>>

Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Freeman1978; @Lai2012].
Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
Considering the relationship between this property and TL in the food web of the MPA N-BB, it is worth to highlight that species with the highest closeness values are low-TL consumers (TL = 2 - 3): species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda. Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], and the warming trend reported for the surface and subsurface waters in the Southwest Atlantic Ocean [@Franco2020a; @Galvan2022a], should be of concern since it might reach many other species in the food web.
Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010]. We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense. Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides* (juveniles), the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem. All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
